Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2015-01-30 papers/wdmerger_I/paper.tex
Move the bibliography file up to the main papers subdirectory so that it can be included in any file that needs references.
Do the same for the apj bibliography style file.
Add discussion to paper of starting timestep size.

@@

\bibliographystyle{apj}
\bibliography{refs}

>>>>

As a consequence of starting in a non-equilibrium setting, there are 
large density and pressure gradients near the white dwarf surfaces
that result in large amounts of mass flowing into the ambient
medium. This can result in spurious non-physical consequences such as 
the total density or energy going negative in a zone. To compensate 
for this, we start the simulation with a timestep that is a few orders 
of magnitude smaller than that required by the CFL criterion, and allow
the timestep to increase by 1\% each timestep so that the timestep reaches 
its maximum allowed by the velocities on the grid over a span of approximately 
1000 timesteps. This allows the ambient medium just outside the white dwarf
to come closer to equilibrium with the surface without having 
discontinuous jumps in the density or energy. For all simulations, 
the maximum timestep is set to be equal to one-half of the CFL limit.

@@

\bibliographystyle{../apj}
\bibliography{../refs}
